Causal Compatability Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-14 documents/TriangleScenario/ts.tex
Updates from ShareLaTeX

    \todo[TC]{Flesh out document from archive}

>>>>

    \section{Introduction}
    \begin{itemize}
        \item \todo[TC]{Overview of importance of inequalities}
        \item \todo[TC]{Triangle Scenario and existing work}
        \item \todo[TC]{Objective of research project}
        \item \todo[TC]{Structure of this paper}
    \end{itemize}

    \section{Causal Compatibility}
    \begin{itemize}
        \item \todo[TC]{Define marginal scenario}
        \item \todo[TC]{Define marginal model}
        \item \todo[TC]{Define causal structure}
        \item \todo[TC]{Define compatibility}
    \end{itemize}

    \section{Triangle Scenario}
    \begin{itemize}
        \item \todo[TC]{Discuss some of its appearances in other work}
        \item \todo[TC]{Figure}
    \end{itemize}
    \subsection{Fritz Distribution}
    \begin{itemize}
        \item \todo[TC]{Reproduce Fritz Distribution}
        \item \todo[TC]{Recall its proof of incompatibility}
        \item \todo[TC]{Requires perfect correlations}
        \item \todo[TC]{Not robust to noise}
        \item \todo[TC]{Fritz Problem 2.17}
    \end{itemize}
    \section{Inflation Technique}
    \begin{itemize}
        \item \todo[TC]{Summarize inflation technique}
        \item \todo[TC]{Inflations of Triangle Scenario}
        \item \todo[TC]{Demonstrate that one can derive causal incompatibility inequalities from inflation}
        \item \todo[TC]{Pre-injectable sets for Large inflation}
    \end{itemize}

    \section{Deriving Inequalities}
    \begin{itemize}
        \item \todo[TC]{Marginal problem}
        \item \todo[TC]{Popular methods: Fourier Motzkin (Convex hull, Polytope projection), Hardy implication inequalities, linear program/certificate}
        \item \todo[TC]{Overview incidence for Large Inflation}
        \item \todo[TC]{Rule out expensive methods like FM}
        \item \todo[TC]{Present some of the inequalities found}
    \end{itemize}

    \subsection{Symmetric Inequalities}
    \begin{itemize}
        \item \todo[TC]{Discuss symmetries and why they are useful}
        \item \todo[TC]{Symmetrizing Incidence Matrix}
        \item \todo[TC]{Large inflation incidence contracted drastically}
        \item \todo[TC]{Present some of the inequalities found}
    \end{itemize}

    \section{Violations}
    \begin{itemize}
        \item \todo[TC]{Fritz Distribution violates found inequalities}
    \end{itemize}
    \subsection{Numerical Optimizations}
    \begin{itemize}
        \item \todo[TC]{Generic idea}
        \item \todo[TC]{Optimization techniques used}
    \end{itemize}
    \subsection{Parameterizing Quantum Distributions}
    \begin{itemize}
        \item \todo[TC]{Unitaries}
        \item \todo[TC]{States}
        \item \todo[TC]{Measurements}
        \item \todo[TC]{Aligning States / Permutation}
    \end{itemize}
    \subsection{Results}
    \begin{itemize}
        \item \todo[TC]{Plots of various optimizations}
        \item \todo[TC]{Features of maximally violating distributions}
    \end{itemize}

    \section{Conclusions}
    \begin{itemize}
        \item \todo[TC]{Inflation technique capable of finding inequalities witnessing quantum/classic difference in TS}
        \item \todo[TC]{Causal incompatibility inequalities found violated by known distributions}
        \item \todo[TC]{Maximal distributions are different than Fritz but still rely on Bell's theorem}
        \item \todo[TC]{Refinement on Fritz's question}
    \end{itemize}

    \section*{Acknowledgments}
    \begin{itemize}
        \item \todo[TC]{Elie}
        \item \todo[TC]{Perimeter}
        \item \todo[TC]{University of Waterloo}
        \item \todo[TC]{Possible due to Mike Lazaridis Scholarship}
    \end{itemize}
